New_Data_Coherence

### 2019-09-20 Analysis/Coherence_Calculations_New.Rmd
Add minimum num_genes

@@

#STRING
dis_slopes_string_count = disease_overall_string %>% filter(Internal != 0) %>%
    group_by(Disease, Category) %>% mutate(Count = n()) %>% group_by(Disease, Category, Count) %>%
    do({
      mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
      data.frame(Slope= coef(mod)[1])
    }) %>% arrange(Slope) %>% filter(Count>4)

#STRING Filtered
dis_slopes_string_filt_count = disease_overall_string_filt %>% filter(Internal != 0) %>%
    group_by(Disease, Category) %>% mutate(Count = n()) %>% group_by(Disease, Category, Count) %>%
    do({
      mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
      data.frame(Slope= coef(mod)[1])
    }) %>% arrange(Slope) %>% filter(Count>4)

#BIOGRID
dis_slopes_biogrid_count = disease_overall_biogrid %>% filter(Internal != 0)  %>%
    group_by(Disease, Category) %>% mutate(Count = n()) %>% group_by(Disease, Category, Count) %>%
    do({
      mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
      data.frame(Slope= coef(mod)[1])
    }) %>% arrange(Slope) %>% filter(Count>4)

>>>>

```{r}
# Minimum number of genes having non-zero internal edges for a network to be processed
num_genes = 10
```

@@

#STRING
dis_slopes_string_count = disease_overall_string %>% filter(Internal != 0) %>%
    group_by(Disease, Category) %>% mutate(Count = n()) %>% group_by(Disease, Category, Count) %>%
    do({
      mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
      data.frame(Slope= coef(mod)[1])
    }) %>% arrange(Slope) %>% filter(Count > num_genes)

#STRING Filtered
dis_slopes_string_filt_count = disease_overall_string_filt %>% filter(Internal != 0) %>%
    group_by(Disease, Category) %>% mutate(Count = n()) %>% group_by(Disease, Category, Count) %>%
    do({
      mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
      data.frame(Slope= coef(mod)[1])
    }) %>% arrange(Slope) %>% filter(Count > num_genes)

#BIOGRID
dis_slopes_biogrid_count = disease_overall_biogrid %>% filter(Internal != 0)  %>%
    group_by(Disease, Category) %>% mutate(Count = n()) %>% group_by(Disease, Category, Count) %>%
    do({
      mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
      data.frame(Slope= coef(mod)[1])
    }) %>% arrange(Slope) %>% filter(Count > num_genes)
